### 2017-01-26 docs/ms_communitySynchrony_PREPRINT.tex
just committing things to this branch to get out

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{\color{red}\textsf{THIS MANUSCRIPT HAS NOT UNDERGONE PEER REVIEW}}
\lhead{}
\rhead{}

@@

\thispagestyle{fancy}
\begin{singlespace}

\begin{center}
\large{\textbf{Environmental responses, not species interactions, determine species synchrony in natural plant communities}}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}\footnote{Correspondence: Email: atredenn@gmail.com}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\begin{abstract}
Temporal asynchrony among species \textcolor{blue}{helps}\footnote{\textcolor{blue}{Changes and insertions unique to this version are shown in blue text.}} diversity \textcolor{blue}{to} stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific \textcolor{blue}{interactions}, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
\textcolor{blue}{We found} that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific \textcolor{blue}{interactions} and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

\vspace{2em}

\noindent{}\textbf{Keywords}\\
\noindent{}synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability
\end{abstract}

@@

\subsection{INTRODUCTION}\label{introduction}

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding \textcolor{blue}{in different ways} to environmental
fluctuations (environmental stochasticity), or fluctuating
asynchronously because of random chance events (demographic
stochasticity) (Isbell et al. 2009, Hector et al. 2010, {{de
Mazancourt}} et al. 2013). Species richness affects synchrony because
larger species pools are more likely to contain species that respond
disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014).
\textcolor{blue}{The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.}

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
\textcolor{blue}{interspecific interactions} (Loreau and {{de
Mazancourt}} 2008, 2013, Gonzalez and Loreau 2009). For example, in a
community composed of large \textcolor{blue}{populations} (no
demographic stochasticity)
\textcolor{blue}{with weak interspecific interations}, community-wide
species synchrony should be determined by the covariance of species'
responses to the environment (Loreau and {{de Mazancourt}} 2008).
However, \textcolor{blue}{this} prediction relies on a relatively simple
population model and only holds under two assumptions: (i) species'
responses to the environment are similar in magnitude and (ii) all
species have similar growth rates.
\textcolor{blue}{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical is unkown because few studies have explicitly tested theory on the drivers of species synchrony in natural communities}
(Mutshinda et al. 2009, Thibaut et al. 2012),
\textcolor{blue}{and they did not consider demographic stochasiticity.}

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from
\textcolor{blue}{the covariance matrix of species abundances} (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific
\textcolor{blue}{interactions} is to remove them one-by-one, and in
combination. In principle, this could be done in an extremely controlled
laboratory setting, but empirically-based models of interacting
populations, fit with data sets from natural communities, offer a
practical alternative. For example, Mutshinda et al. (2009) fit a
dynamic population model to several community time series of insect and
bird abundances. They used a statistical technique to decompose temporal
variation into competition and environmental components, and found that
positively correlated environmental responses among species determined
community dynamics. Thibaut et al. (2012)
\textcolor{blue}{used a similar approach for reef fish and came to a similar conclusion: environmental responses determine synchrony.}
While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although both studies quantified the
relative importance of environmental stochasticity and
\textcolor{blue}{interspecific interactions} to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
species synchrony in natural plant communities. To achieve these
objectives, we first refine theory that has been used to predict the
effects of species richness on ecosystem stability ({{de Mazancourt}} et
al. 2013) and species synchrony (Loreau and {{de Mazancourt}} 2008) to
generate predictions of community-wide species synchrony under two
limiting cases derived from the dynamics of individual species in
monoculture. We then confront our theoretical predictions with
simulations from the empirically-based population models. Second, we use
the multi-species population models to perform simulation experiments
that isolate the effects of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

\subsection{THEORETICAL MODEL}\label{theoretical-model}

\subsubsection{The model}\label{the-model}

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases.
\textcolor{blue}{The limiting case predictions we derive serve as baselines to help us interpret results from empirically-based simulations (described below).}
We focus on synchrony of per capita growth rates, rather than
abundances, because growth rates represent the instantaneous response of
species to the environment and competition, and are less susceptible to
the legacy effects of drift and disturbance (Loreau and {{de
Mazancourt}} 2008). We present equivalent results for synchrony of
species abundances in the Online Supporting Information, and show that
they lead to the same overall conclusions as synchrony of per capita
growth rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information).
\textcolor{blue}{Due to the linear approximation approach, our analytical predictions will likely fail in communities where species exhibit large fluctuations due to limit cycles and chaos}
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Indeed, one of the advantages of focusing on growth rates rather than abundances is that growth rates are more likely to be well-regulated around an equilibrium value, if the long-term average of a species' growth rate is relatively small}
(e.g., \(r < 2\)).

\subsubsection{Predictions}\label{predictions}

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction
\textcolor{blue}{for the synchrony of per capita growth rates for $\mathcal{M}_{D}$, $\phi_{R,\mathcal{M}_{D}}$, is}

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}. Confronting our theoretical predictions with data
requires estimates of species dynamics of large populations (no
demographic stochasticity) \textcolor{blue}{growing in isolation} (no
interspecific interactions) to calculate the covariance of species'
environmental responses. To estimate environmental responses in natural
communities, we turn to our population models built using long-term
demographic data.

\subsection{EMPIRICAL ANALYSIS}\label{empirical-analysis}

\subsubsection{Materials and methods}\label{materials-and-methods}

\paragraph{Data}\label{data}

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal variance of species
\emph{i'}s per capita population growth rate (\(r_i\)) and
\(\sigma^{2}_{T}\) is the temporal variance of the aggregate
community-level growth rate. \(\phi\) ranges from 0 at perfect
asynchrony to 1 at perfect synchrony (Loreau and {{de Mazancourt}}
2008). We use the same equation to calculate observed synchrony of
species' percent cover, which we present to relate our results to
previous findings, even though we focus on synchrony of growth rates in
our model simulations (see below).

\paragraph{Fitting statistical models}\label{fitting-statistical-models}

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013).
\textcolor{blue}{Crowding was treated as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including yearly crowding effects did not change our results.}
Spatial (quadrat groupings) variation was treated as a random effect on
the intercept and temporal (interannual) variation was treated as random
effects on the intercept and the effect of genet size in the previous
year (Online Supporting Information).

@@

\paragraph{Building dynamic multi-species
models}\label{building-dynamic-multi-species-models}

Once we have fit the vital rate statistical models, building the
population models is straightforward. For the IBM, we initialize the
model by randomly assigning plants spatial coordinates, sizes, and
species identities until each species achieves a density representative
of that observed in the data. We then project the model forward by using
the survival regression to determine whether a genet lives or dies, the
growth regression to calculate changes in genet size, and the
recruitment regression to add new individuals that are distributed
randomly in space. Crowding is directly calculated at each time step
since each genet is spatially referenced (as in the observed data).
Environmental stochasticity is not an inherent feature of IBMs, but is
easily included since we fit year-specific temporal random effects for
each vital rate regression. To include temporal environmental variation,
at each time step we randomly choose a set of estimated survival,
growth, and recruitment parameters specific to one observation year. For
all simulations, we ignore the spatial random effect associated with
variation among quadrat groups, so our simulations represent an average
quadrat for each site.

The IPM uses the same vital rate regressions as the IBM (Rees and Ellner
2009, Rees et al. 2014), but it is spatially implicit and does not
include demographic stochasticity. Following Chu and Adler (2015), we
use a mean field approximation that captures the essential features of
spatial patterning to define the crowding index at each time step
(Supporting Online Information). Temporal variation is included in
exactly the same way as for the IBM. For full details on the IPMs we
use, see Chu and Adler (2015).

\paragraph{Simulation experiments}\label{simulation-experiments}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{\color{red}\textsf{preprint}}
\usepackage{titlesec}
\titleformat{\section}{\normalsize\sc\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\it\centering}{\thesubsection}{1em}{}
\titleformat*{\paragraph}{\normalsize\it}
\lhead{}
\rhead{}

@@

\thispagestyle{fancy}

\definecolor{blue}{gray}{0}

\begin{singlespace}

\begin{center}
\large{\textbf{Environmental responses, not species interactions, determine \textcolor{blue}{synchrony of dominant species in semiarid grasslands}}}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\begin{abstract}
Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative \textcolor{blue}{influence} of these factors \textcolor{blue}{on the synchrony of dominant species in five semiarid grasslands.}
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. 
\textcolor{blue}{For the dominant species in these plant communities}, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

\emph{Key words: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability, grassland}

\end{abstract}

@@

\section{Introduction}

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010).
\textcolor{blue}{The stabilizing effect of species richness arises from a combination of selection effects and complementarity}
(Loreau and Hector 2001).
\textcolor{blue}{Selection effects occur when a dominant species has lower than average temporal variability, which generates a positive effect on ecosystem stability}
(e.g., Grman et al. 2010).
\textcolor{blue}{Complementarity occurs when species have unique temporal dynamics, causing their abundances to fluctuate asynchronously, increasing ecosystem stability.}
\textcolor{blue}{The premise of this paper is that understanding the mechanisms driving species' temporal dynamics, and resulting (a)synchrony, is necessary to predict the impacts of global change on ecosystem stability.}

\textcolor{blue}{Asynchronous dynamics, also known as compensatory dynamics}
(Gonzalez and Loreau 2009),
\textcolor{blue}{occur whenever species synchrony is not perfect} and
result from individual species responding in different ways to
environmental fluctuations, random chance events, and/or competitive
interactions (Isbell et al. 2009, Hector et al. 2010, {{de Mazancourt}}
et al. 2013, Gross et al. 2014). Species richness affects
\textcolor{blue}{the degree of synchrony in a community} because larger
species pools are more likely to contain species that respond
dissimilarly to environmental conditions, reducing synchrony and
increasing stability (Yachi and Loreau 1999).
\textcolor{blue}{Species richness can also affect synchrony if the strength of species interactions varies systematically with richness, because competition generally increases synchrony and reduces stability}
(Loreau and {{de Mazancourt}} 2013, but see Gross et al. 2014).

\textcolor{blue}{The effects of environmental change and species losses on ecosystem stability will depend on whether synchrony is driven by species-specific responses to environmental conditions or interspecific competition}
(Hautier et al. 2014).
\textcolor{blue}{If responses to environment are important, then environmental change could alter synchrony and stability.
If competition is important, then the direct effects of environmental change may not affect synchrony and stability, but species gains/losses will.}

\textcolor{blue}{The relative role of environmental responses and competition in driving synchrony  in natural plant communities}
remains controversial (reviewed in Gonzalez and Loreau 2009). One source
of the controversy is that quantifying the relative strengths of each
driver based on the covariance matrix of species abundances (e.g.,
Houlahan et al. 2007) is impossible. This is because observed synchrony
can arise from non-unique combinations of factors (Ranta et al. 2008).
For example, weak synchrony of population abundances could reflect
positive environmental correlations (synchronizing effect) offset by
strong competition (desynchronizing effect), or negative environmental
correlations and weak competition.

\textcolor{blue}{Theory can help us resolve this empirical question.}
Recent theoretical work has identified three determinants of species
synchrony: environmental stochasticity, interspecific interactions, and
demographic stochasticity (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009).
\textcolor{blue}{This theory has been developed by focusing on simple limiting cases in which only one of these three drivers operates.}
For example, in a community composed of large populations (no
demographic stochasticity) with weak interspecific interations,
community-wide species synchrony should be determined by the covariance
of species' responses to the environment (Loreau and {{de Mazancourt}}
2008). However, this prediction relies on a relatively simple population
model and \textcolor{blue}{depends on two restrictive} assumptions: (i)
species' responses to the environment are similar in magnitude and (ii)
all species have similar growth rates. Whether such theoretical
predictions hold in natural communities where species differences are
unlikely to be symmetrical is unkown because few studies have explicitly
tested theory on the drivers of species synchrony in natural communities
(Mutshinda et al. 2009, Thibaut et al. 2012), and they did not consider
demographic stochasiticity.

An intuitive way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific interactions is to remove
them one-by-one, and in combination.
\textcolor{blue}{If synchrony changes more when we remove environmental stochasticity than when we remove interspecific interactions, we would conclude that environmental fluctuations are the more important driver.}
In principle, this could be done in an extremely controlled laboratory
setting (e.g., Venail et al. 2013), but empirically-based models of
interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that positively correlated environmental responses among species
determined community dynamics. Thibaut et al. (2012) used a similar
approach for reef fish and came to a similar conclusion: environmental
responses determine synchrony.

While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique does have some limitations.
\textcolor{blue}{First, although both studies quantified the relative importance of environmental stochasticity and interspecific interactions to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony would change if each factor were removed.
Second, they relied on popluation abundance data that may or may not reliably capture competitive interactions occuring at the individual level.
Third, fluctuations in abundance may mask the mechanisms that underpin species synchrony.
The synchrony of species' abundances ultimately determines the stability of total community biomass, but the processes that drive species synchrony are most tightly linked to each species' immediate response to environmental conditions and competition}
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Therefore, we focus on per capita growth rates, which represent a species' immediate response to interannual fluctuations.}

Here, we use multispecies population models fit to long-term demographic
data from five semi-arid plant communities to test theory on the drivers
of species synchrony (Fig. 1). Our objectives are to (1) derive and test
theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, interspecific
interactions, and demographic stochasticity on
\textcolor{blue}{the synchrony of dominant species} in natural plant
communities.
\textcolor{blue}{While our focus is limited to dominant species due to data constraints, previous work indicates that the dynamics of dominant species determine ecosystem functioning in grasslands}
(Smith and Knapp 2003, Bai et al. 2004, Grman et al. 2010, Sasaki and
Lauenroth 2011).

To achieve our objectives, we first refine theory that has been used to
predict the effects of species richness on ecosystem stability ({{de
Mazancourt}} et al. 2013) and species synchrony (Loreau and {{de
Mazancourt}} 2008) to generate predictions of community-wide species
synchrony under two limiting cases. We then confront our theoretical
predictions with simulations from the empirically-based population
models. Second, we use the multi-species population models to perform
simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific interactions
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine synchrony
\textcolor{blue}{of dominant species} in our focal grassland
communities.

\section{Theoretical Model}\subsection{The model}

While existing theory has identified
\textcolor{blue}{environmental responses, species interactions, and demographic stochasticity as the drivers of the temporal synchrony,}
we do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates.

Following Loreau and {{de Mazancourt}} (2008) and {{de Mazancourt}} et
al. (2013), we define population growth, ignoring observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the
\textcolor{blue}{temporal variance of species \emph{i}'s response to the environment and $u_{ei}(t)$ is a normal variable with unit variance that is independent among species but may be correlated.}
\textcolor{blue}{The product, $\sigma_{ei}u_{ei}(t)$, is species \emph{i}'s environmental response.}
Demographic stochasticity arises from variations in births and deaths
among individuals (e.g., same states, different fates), and is included
in the model as a first-order, normal approximation (Lande et al. 2003,
{{de Mazancourt}} et al. 2013). \(\sigma_{di}^2\) is the demographic
variance
(\textcolor{blue}{i.e., the intrinsic demographic stochasticity of species \emph{i}})
and \(u_{di}(t)\) are independent normal variables with zero mean and
unit variance
\textcolor{blue}{that allow demographic stochasiticity to vary through time.}

To derive analytical predictions we solved a first-order approximation
of Equation 2 ({{de Mazancourt}} et al. 2013 and Appendix S1). Due to
the linear approximation approach, our analytical predictions will
likely fail in communities where species exhibit large fluctuations due
to limit cycles and chaos (Loreau and {{de Mazancourt}} 2008). Indeed,
one of the advantages of focusing on growth rates rather than abundances
is that growth rates are more likely to be well-regulated around an
equilibrium value, if the long-term average of a species' growth rate is
relatively small (e.g., \(r < 2\)).

\subsection{Predictions}

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction for the synchrony of per capita
growth rates for \(\mathcal{M}_{D}\), \(\phi_{R,\mathcal{M}_{D}}\), is

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}.

Confronting our theoretical predictions with data requires estimates of
species dynamics of large populations (no demographic stochasticity)
growing in isolation (no interspecific interactions) to calculate the
covariance of species' environmental responses. To estimate
environmental responses in natural communities, we turn to our
population models built using long-term demographic data.

\section{Empirical Analysis}\subsection{Materials and methods}

\paragraph{Data.--}\label{data.}

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal
\textcolor{blue}{standard deviation} of species \emph{i'}s per capita
population growth rate (\(r_i\)) and \(\sigma^{2}_{T}\) is the temporal
variance of the aggregate community-level growth rate. \(\phi\) ranges
from 0 at perfect asynchrony to 1 at perfect synchrony (Loreau and {{de
Mazancourt}} 2008). We use the same equation to calculate observed
synchrony of species' percent cover, which we present to relate our
results to previous findings, even though we focus on synchrony of
growth rates in our model simulations (see below).

\paragraph{Fitting statistical
models.--}\label{fitting-statistical-models.}

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Spatial (quadrat groupings) variation was treated as a random
effect on the intercept and temporal (interannual) variation was treated
as random effects on the intercept and the effect of genet size in the
previous year (Appendix S1).

\textcolor{blue}{Interspecific and intraspecific crowding, which represent species interactions, can be included as fixed effects or as random effects that vary each year.
Strong year-to-year variation in these crowding effects would indicate a statistical interaction between environmental conditions and species interactions.
We tested for such a dynamic by comparing models with and without random year effects on crowding.
Based on the results, we decided to treat crowding as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including interannual variation in crowding did not change our results.}

@@

\paragraph{Building dynamic multi-species
models.--}\label{building-dynamic-multi-species-models.}

Once we have fit the vital rate statistical models, building the
population models is straightforward. For the IBM, we initialize the
model by randomly assigning plants spatial coordinates, sizes, and
species identities until each species achieves a density representative
of that observed in the data. We then project the model forward by using
the survival regression to determine whether a genet lives or dies, the
growth regression to calculate changes in genet size, and the
recruitment regression to add new individuals that are distributed
randomly in space. Crowding is directly calculated at each time step
since each genet is spatially referenced. Environmental stochasticity is
not an inherent feature of IBMs, but is easily included since we fit
year-specific temporal random effects for each vital rate regression. To
include temporal environmental variation, at each time step we randomly
choose a set of estimated survival, growth, and recruitment parameters
specific to one observation year. For all simulations, we ignore the
spatial random effect associated with variation among quadrat groups, so
our simulations represent an average quadrat for each site.

The IPM uses the same vital rate regressions as the IBM, but it is
spatially implicit and does not include demographic stochasticity.
Following Chu and Adler (2015), we use a mean field approximation that
captures the essential features of spatial patterning to define the
crowding index at each time step (Supporting Online Information).
Temporal variation is included in exactly the same way as for the IBM.
For full details on the IPMs we use, see Chu and Adler (2015).

\paragraph{Simulation experiments.--}\label{simulation-experiments.}

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific interactions)
were removed one-by-one and in combination. To remove interspecific
interactions, we set the off-diagonals of the interaction matrix for
each vital rate regression to zero. This retains intraspecific
interactions, and thus density-dependence, and results in simulations
where species are growing in isolation. We cannot definitively rule out
the effects of species interactions on all parameters, meaning that a
true monoculture could behave differently than our simulations of a
population growing without interspecific competitors. To remove the
effect of a fluctuating environment, we removed the temporal
(interannual) random effects from the regression equations. To remove
the effect of demographic stochasticity, we use the IPM rather than the
IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Results from an IBM with infinite population size would
converge on results from the IPM. Given computational constraints, the
largest landscape we simulate is a 25 \(\text{m}^2\) plot.
